Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-21 ms.tex
more on absolute zero level

Because of these ambiguities in the relationship between 857 GHz and 
H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level
by comparison to the FDS99 857 GHz prediction. This renders the \PLANCK~857 GHz
absolute zero level tied largely to the reliable FIRAS zero point, and to some 
lesser extent to H\,\textsc{i} through the \verb|i100| zero point. 
Specifically, we fit a linear model to the FDS99 predicted 857 GHz values as a 
function of \PLANCK~857 GHz. We used a version of the \PLANCK~857 GHz map with 
zodiacal light and point sources removed and smoothed to 1$^{\circ}$ 
resolution, which we will refer to as $\mathcal{I}_{857}$. For this analysis, 
we considered $\mathcal{I}_{857}$ to be the independent variable, as it has 
much higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not a monochromatic 
prediction, as we have incorporated the finite bandpass correction factors 
described in $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine
the dust spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels 
with $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to 
degree resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure XX shows a scatterplot of $\mathcal{I}_{857}$ 
versus $\mathcal{F}_{857}$, with a moving median and linear fit overplotted.
The linear fit was performed with uniform weights and iterative outlier
rejection. It is encouraging that the slope is quite close to unity, and 
the offset near zero.

The formal statistical errors on these parameters are small. Undoubtedly,
just as in the case of performing the regression versus  H\,\textsc{i}, 
systematic issues will dominate the uncertainty in the derived zero point
offset. Specifically, the likely culprits are imperfect zodiacal light 
corrections and the FDS99 temperature map. To quantify the level of systematic
error

@@

% mention use of bandpass correction factors when doing Planck vs. prediction
% regressions

@@

\section{Conclusion}
\label{sec:conclusion}

>>>>

Because of these ambiguities in the relationship between 857 GHz and 
H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level
by comparison to the FDS99 857 GHz prediction. This renders the \PLANCK~857 GHz
absolute zero level tied largely to the reliable FIRAS zero point, and to some 
lesser extent to H\,\textsc{i} through the \verb|i100| zero point. 
Specifically, we fit a linear model to the FDS99 predicted 857 GHz values as a 
function of \PLANCK~857 GHz. We used a version of the \PLANCK~857 GHz map with 
zodiacal light and point sources removed and smoothed to 1$^{\circ}$ 
resolution, which we will refer to as $\mathcal{I}_{857}$. For this analysis, 
we considered $\mathcal{I}_{857}$ to be the independent variable, as it has 
much higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not a monochromatic 
prediction, as we have incorporated the finite bandpass correction factors 
described in $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine
the dust spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels 
with $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to 
degree resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure XX shows a scatterplot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.994$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
the slope is quite close to unity, and the offset near zero.

The formal statistical errors on these parameters are small. Just as in the 
case of performing the regression versus  H\,\textsc{i}, 
systematic issues will dominate the uncertainty in the derived zero point
offset. The likely culprits in this case are imperfect zodiacal light 
corrections and the FDS99 temperature map. To quantify the level of systematic
error, we split the sky into four quadrants, with the dividing boundaries
being $b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again
restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the 
regression in each quadrant. The slopes varied from 0.948 to 0.993, with an
rms of 0.0188, while the offsets varied from $-$0.056 MJy/sr to $+$0.089 
MJy/sr, with an rms of 0.0586 MJy/sr.

% Maybe it's not necessary to mention the 545 GHz check ... although
% i should do the check eventually as to whether choosing 545 GHz
% for the absolute zero point is consistent with choosing 857 GHz
% to within the errors that i'm quoting

%We also repeated the full-sky FDS99 prediction versus \PLANCK~regression at 
%545 GHz. After

%We also repeated the full-sky and quadrant regressions with the FDS99 
%predictions at 545 GHz (see bottom panel of Figure XX). We find the 
%slopes vary from XX to YY with an rms scatter of ZZ. The 545 GHz zero points
%have an rms scatter of SS, which is consistent with the 545 GHz zero 
%point rms implied by the scatter in 857 GHz zero point.

@@

@@

\section{Conclusion}

% should mention that one definitive improvement of this work relative
% to FDS99 is that there are uncertainty/covariances provided for
% the derived parameters !!!!

\label{sec:conclusion}
